### 2016-04-19 text/ms.Rmd
Edit main text

<!-- TODO
- [ ] trash slope?
- [ ] trash covariates?
- [ ] add discussion of uncertainty (CIs) and ML (and incorporating uncertainty into pred.)
- [ ] add table of fish methods and ensemble models
- [ ] add flow chart of cross validation / methods
-->

@@

\tableofcontents

@@

Population status and trend are two of the most fundamental values to quantify
in fisheries management. However, fisheries managers are often faced with
reconciling multiple uncertain and potentially conflicting estimates of status
and trend [e.g. @brodziak2010; @branch2011; @deroba2015]. For example, some
models may suggest a population is at risk and declining in abundance while
others may suggest it is not at risk and stable.

@@

We can exploit these characteristics by using the predictions from a group of
models as inputs into a separate statistical model. This technique, sometimes
called superensemble modelling [@krishnamurti1999], is common in climate and
weather forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to a
training dataset where outcomes are well known and then used to predict on a
dataset of interest (Fig. \ref{didactic}). For example, @krishnamurti1999
combined predictions of wind and precipitation in Asian monsoons via a
superensemble regression fit to observed data. Their superensemble was
considerably more accurate than any individual prediction or weighted average
of predictions.

@@

@@

The superensemble models were able to improve the predictive performance by
harnessing the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were approximately
linearly related to $B/B_\mathrm{MSY}$ within the low and high clusters of
predictions (Fig. \ref{partial-sim}). Superensembles also exploited the
covariance between individual model predictions. For instance, both the linear
model and GBM ensemble suggest that if mPRM and SSCOM predict high status, the
true status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l).
The addition of spectral density covariates helped the superensemble models
correctly predict higher status values (Fig. \ref{hexagon}g, h) due to the
interactions between the spectral density predictors and the individual model
predictors (Fig. \ref{partial-2d-sim}). Although the additional covariates
improved ensemble fit, performance of the ensembles was only marginally degraded
by removing these covariates (Fig. \ref{hexagon} vs. Fig.
\ref{hexagon-sim-basic}).

>>>>

<!-- TODO
- [ ] add discussion of uncertainty (CIs) and ML (and incorporating uncertainty into pred.)
- [ ] add back in the roc plot and sentence in the main text
- [ ] rerun the main simulation analysis because the equations of change for the slope
-->

@@

<!-- \tableofcontents -->

@@

Status and trend are two of the most fundamental values to quantify in the
management of ecological populations [e.g. @iucn2015]. However, managers are
often faced with reconciling multiple uncertain and potentially conflicting
estimates of status and trend [e.g. @brodziak2010; @branch2011; @deroba2015].
For example, one models may suggest a population is at risk and declining in
abundance while others may suggest it is not at risk and stable.

@@

We can exploit these characteristics by using the predictions from a group of
models as inputs into a separate statistical model. This technique, sometimes
called superensemble modelling [@krishnamurti1999], is common in climate and
weather forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to a
training dataset where outcomes are well known and then used to predict on a
dataset of interest. For example, @krishnamurti1999
combined predictions of wind and precipitation in Asian monsoons via a
superensemble regression fit to observed data. Their superensemble was
considerably more accurate than any individual prediction or weighted average
of predictions.

@@

<!--TODO Add in the reference to (Fig. \ref{didactic}) and reorder the figures and add
in the figure with the partial dependence -->

@@

The superensemble models were able to improve the predictive performance by
harnessing the best properties of individual models, the covariance between
individual models, and interactions with other covariates. For example, SSCOM
had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig.
\ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were
approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high
clusters of predictions (Fig. \ref{partial-sim}). Superensembles also exploited
the covariance between individual model predictions. For instance, both the
linear model and GBM ensemble suggest that if mPRM and SSCOM predict high
status, the true status also tends to be high (Figs \ref{lm-coefs},
\ref{partial-2d-sim}l). The addition of spectral density covariates helped the
superensemble models correctly predict higher status values (Fig.
\ref{hexagon-sim-covariance}g, h). The performance of the ensembles was only
marginally improved by including these covariates (Fig.
\ref{performance-with-covariance} vs. Fig. \ref{performance}.
